GM12878 General Read Sequence Figure Generation

### 2022-05-31 R/GM12878GeneralReadSequenceDataGeneration.rmd
Added GM12878 cisplatin notebooks

---
title: "E coli WT General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

expansionOffset = 10
cellType = "E_coli_WT"
CPDTimepoints = list(`5min` = NULL)
minReadLength = 11; maxReadLength = 13

@@

```{r compute_and_write_CPD_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(CPDTimepoints)) {
    singleFileFullAnalysis("CPD", repitition, timepoint)
  }
}
```

>>>>

---
title: "GM12878 General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

expansionOffset = 10
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r compute_and_write_cisplatin_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(CisplatinTimepoints)) {
    singleFileFullAnalysis("cisplatin", repitition, timepoint)
  }
}
```

### 2022-05-31 R/GM12878GeneralReadSequenceFigureGeneration.rmd
Added GM12878 cisplatin notebooks

---
title: "E coli WT General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

```{r read_sequence_frequencies}
CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDTGGSeqFreq)) {
  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDTGGSeqFreq)[i],
      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(CPDCGASeqFreq$rep1,
                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(CPDCGASeqFreq$rep2,
                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

@@

```{r CPD_read_length_frequencies}
readAndPlotReadLengthFrequencies("CPD", "rep1", CPDTimepoints)
readAndPlotReadLengthFrequencies("CPD", "rep2", CPDTimepoints)
```

>>>>

---
title: "GM12878 General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

```{r read_sequence_frequencies}
CisplatinTGGSeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinTGGSeqFreq)) {
  for (j in seq_along(CisplatinTGGSeqFreq[[i]])) {
    CisplatinTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinTGGSeqFreq)[i],
      timepoint = names(CisplatinTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CisplatinCGASeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinCGASeqFreq)) {
  for (j in seq_along(CisplatinCGASeqFreq[[i]])) {
    CisplatinCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinCGASeqFreq)[i],
      timepoint = names(CisplatinCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(CisplatinTGGSeqFreq$rep1,
                        title = "cisplatin TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CisplatinTGGSeqFreq$rep2,
                        title = "cisplatin TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(CisplatinCGASeqFreq$rep1,
                        title = "cisplatin CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(CisplatinCGASeqFreq$rep2,
                        title = "cisplatin CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

@@

```{r cisplatin_read_length_frequencies}
readAndPlotReadLengthFrequencies("cisplatin", "rep1", CisplatinTimepoints)
readAndPlotReadLengthFrequencies("cisplatin", "rep2", CisplatinTimepoints)
```
